Cross-validation of regression models: mixed model examples (edited v3)

### 2024-09-16 scratch/JSS-submission/Revision-1/Fox-Monette-cv-package.Rmd
add footnote on cvInfo() and as.data.frame() to JSS paper

Applying \code{selectModelList()} to the \code{Auto} polynomial-regression models, and using 10-fold CV, we obtain:
```{r meta-CV-polynomials}
metaCV.auto <- cv(selectModelList, data = Auto, 
                  working.model = mlist, save.model = TRUE, 
                       seed = 2120)
summary(metaCV.auto)
brief(m.sel <- cvInfo(metaCV.auto, "selected model"))
cv(m.sel, seed = 2120)
```
As expected, meta CV produces a larger estimate of MSE for the selected 7th degree polynomial model than CV applied directly to this model (using the same seed for \proglang{R}'s random-number generator to obtain the same folds).

>>>>

Applying \code{selectModelList()} to the \code{Auto} polynomial-regression models, and using 10-fold CV, we obtain:[^cvInfo]
```{r meta-CV-polynomials}
metaCV.auto <- cv(selectModelList, data = Auto, 
                  working.model = mlist, save.model = TRUE, 
                       seed = 2120)
summary(metaCV.auto)
brief(m.sel <- cvInfo(metaCV.auto, "selected model"))
cv(m.sel, seed = 2120)
```

[^cvInfo]: Two functions are employed to access information in objects produced by functions in the \pkg{cv} package: \code{cvInfo()} and \code{as.data.frame()} are generic functions (the latter a standard-\proglang{R} generic) with methods for classes \code{"cv"}, \code{"cvList"}, \code{"cvModlist"}, and \code{"cvSelect"} (in the case of \code{cvInfo()}) , and \code{"cv"}, \code{"cvList"}, and \code{"cvModlist"} (in the case of \code{as.data.frame()}). Here we use \code{cvInfo(metaCV.auto, "selected model")} to retrieve the model selected by \code{cv()} via \code{selectModelList()}. See \code{?cv} and \code{?cvInfo.cvSelect} for details.

As expected, meta CV produces a larger estimate of MSE for the selected 7th degree polynomial model than CV applied directly to this model (using the same seed for \proglang{R}'s random-number generator to obtain the same folds).
